A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-05-29 sections/introduction.tex
Update URL & proof scripts; multi-step relation

\item {\bf A fully mechanized formalization of type inference with
  higher-ranked types:} Our work presents the first fully mechanized formalization
  for type inference of higher ranked types. The formalization is done in the
  Abella theorem prover~\cite{AbellaDesc} and it is available
  online at \url{http://TODO}.\bruno{fill url please!}

>>>>

\item {\bf A fully mechanized formalization of type inference with
  higher-ranked types:} Our work presents the first fully mechanized formalization
  for type inference of higher ranked types. The formalization is done in the
  Abella theorem prover~\cite{AbellaDesc} and it is available
  online at \url{https://github.com/JimmyZJX/TypingFormalization}.\bruno{fill url please!}
